---
title: "Using infra"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{UsingBDSHInfra}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

options(rmarkdown.html_vignette.check_title = FALSE)
```

```{r setup}
library(infra)
```



# Assigning Variable Types
The function `type` can be used to assign the type attribute to a single vector, a column in a `data.frame`, of multiple columns of a `data.frame`. There are a couple ways to use the function depending on the object that the `type` attribute is being assigned. 

The following is a list of the `type`'s that are available. If a type other than these is used, and error is returned.

- id
- y
- y2
- t
- t2
- e
- e2
- x 

## Assign `type` to vector
```{r, error=TRUE}
foo <- rnorm(20)

type(foo) <- "x"
type(foo)

type(foo) <- "error"
```

## Assign `type` to a single `data.frame` column.
```{r}
type(test$usubjid) <- "id"
type(test$usubjid)
```

## Assign `type` to `data.frame`

### Assign to entire `data.frame` 


`value` is assigned by the index of `value` to the corresponding column of x. There are alternative approaches as well.
```{r}
test2 <- test[, 1:6]

type(test2) <- c("id", "id", "id", "x", "x", "x")

# Still need to write this method to display the types for all variables in data.frame
# type(test2)
```


### Using a named vector
```{r}
set.seed(4)
vnames <- sample(names(test), 6)
v <- c("x", "id", "x", "y", "x", "x")
v <- setNames(v, vnames)
v

test2 <- test[, vnames]
type(test2) <- v
# type(test2)
```




### Using the fill option in the method for `data.frame`

In order for the `type` function to work on a `data.frame`, a type must be assigned to every column. Thus the parameters in  `data.frame` method for `type` must be that `length(value) == ncol(x)`, unless the `fill` parameter is used. Using the fill parameter allows you to specify one variable type that is assigned to all the columns which are not explicitly named.
```{r}
v
type(test, fill = "x") <- v
# type(test)
```

<!-- `NA` can also be used as a fill value to exclude unused variables. -->
<!-- ```{r} -->
<!-- type(test, fill = NA) <- v -->
<!-- ``` -->

